A Case Study in Preserving a High Energy Physics Application

### 2014-02-04 paper.tex
add the table "Script of each Solution"

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1: Email\\ \hline
        \\
        1. Create CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
        2. Install BEAN packages: \\
            \hspace{9pt} https://github.com/cms-ttH/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://dwekptrack... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform actual tau roast program \\ 
        \\ \hline
        Version 2: Script\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
        module load git \\        
        cmsenv \\ 
        cvs login \\
        cvs co UserCode/Bicocca/... \\
        git clone... \\
        scram b -j32 \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        \#the experiment data is from HDFS \\
        roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 3: Fine-Grained Toolkit\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \# list of indirect software dependencies \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cmsenv \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        roaster data/generic\_ttl.yaml \\
        \\ \hline
        Version 4\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \#declaration of environment variables\\
        \#data dependencies\\
        \#direct and indirect software dependencies\\
        \#software build and install commands\\
        \#actual analysis program\\ 
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

>>>>

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1: Email\\ \hline
        \\
        1. Create a CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \\ \hline
        Version 2: Script\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone https://github.com/cms-ttH/BEAN.git \\
        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        version 3: Formulated Script \\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 4: Fine-Grained Toolkit\\ \hline
        \\
        \#description of OS version and hardware architecture \\
        \#list of indirect software dependencies \\
        \# set all environment variables\\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}
